%----------------------------------------------------------------------------------------
%  Packages And Other Document Configurations
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style

% Document margins
\usepackage[left=0.50in,top=0.6in,right=0.5in,bottom=0.6in]{geometry}

% Color and hyperlink packages
\usepackage{xcolor}
\usepackage{hyperref}

% Footnote and margin adjustment packages
\usepackage{footnote}
\usepackage{changepage}

% Fontawesome package for icons
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Tabularx package for custom tables
\usepackage{tabularx}

% Define navyblue color
\definecolor{navyblue}{RGB}{0,54,123}

%----------------------------------------------------------------------------------------
%   Customizations
%----------------------------------------------------------------------------------------

% Define italicitem, bolditem, and plainitem commands
\newcommand{\italicitem}[1]{\item{\textit{#1}}}
\newcommand{\bolditem}[1]{\item{\textbf{#1}}}
\newcommand{\plainitem}[1]{\item{#1}}

% Define user-friendly link command for hyperlinks
\newcommand{\link}[2]{{\href{#1}{#2}}}

\newcommand{\entry}[2]{#1 & #2 \tabularnewline} % Defines an entry with two arguments: #1 for the first column and #2 for the second column

%----------------------------------------------------------------------------------------
%   Define envsection command for defining a new environment section
%----------------------------------------------------------------------------------------

\newcommand{\tableEnv}[2]{%
    \begin{rSection}{#1} % Begin rSection with the given name
        \begin{adjustwidth}{0.0in}{0.1in} % Set the left and right margins
            \begin{tabularx}{\linewidth}{@{} >{\bfseries}l @{\hspace{6ex}} X @{}}
                #2 % Print the content inside the tabularx environment
            \end{tabularx}
        \end{adjustwidth}
    \end{rSection}
}

%----------------------------------------------------------------------------------------
%   Begin document
%----------------------------------------------------------------------------------------

% Set name with navyblue color
\name{\color{navyblue}\normalfont Yash Bhutoria}


\begin{document}
    \centering{\color{navyblue}\fontsize{16}{16}\selectfont Enterprise Cloud Architect}
    \printPersonalInfo{
        \personalInfo{\tag{Location}\info{Dallas, TX} \space \tag{E-mail}\info{yash.bhutoria@celebaltech.com}}
    }
    
    
    %----------------------------------------------------------------------------------------
    %   Professional Summary
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Professional Summary}
        {With over 5 years of experience as a Principal Consultant at Celebal Technologies, I specialize the Azure Cloud Platform, Azure PaaS, Data Engineering, and Serverless technologies. I specialize in developing scalable, robust enterprise-grade integration solutions across various sectors, including energy, sustainability, healthcare, and education. My expertise extends to leading cloud migration, optimizing cloud infrastructure for enhanced performance and security, and championing digital transformation efforts. Known for strong problem-solving, automation, and DevOps skills, I deliver cost-efficient, scalable cloud solutions that effectively bridge IT and business objectives.}
    \end{rSection}
    
    %----------------------------------------------------------------------------------------
    %   Work experience section
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Work experience}
        
        % Current work experience entry
        \begin{rSubsection}{Celebal Technologies Americas, Inc.}{May 2023 - Present}{Principal Consultant, Enterprise Integration}{Dallas, TX}
            \item Architecting and developing enterprise integration solutions on hyperscaler clouds
            \item Creating standards and research for Application Modernization
            \item Managing delivery for high value clients
            \item Growing and mentoring a team of 40+ associates
            \item Technical research, strategic planning and advisory
        \end{rSubsection}

            % Second work experience entry
        \begin{rSubsection}{Gies College of Business - University of Illinois Urbana-Champaign}{Oct 2022 - May 2023}{Graduate Research Assistant}{Champaign, IL}
                \item Evaluated public datasets for Filecoin/IPFS storage suitability
                \item Demonstrated decentralized computing use case over data
                \item Created cost-benefit analytical model for decentralized storage
                \item Provided insights on decentralized storage adoption for universities
        \end{rSubsection}

        % First work experience entry
        \begin{rSubsection}{Celebal Technologies Pvt. Ltd.}{May 2019 - July 2022}{Member of Technical Staff, Enterprise Integration}{Jaipur, India}
            \item Designing and developing data integration solutions on hyperscalers like Azure and GCP
            \item Managing delivery for high value clients
            \item Growing and mentoring a team of 30+ associates
            \item Technical research, strategic planning and advisory
        \end{rSubsection}
        
        
    \end{rSection}
    
    
    %----------------------------------------------------------------------------------------
    %   Education section
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Education}
        
        % Master's degree entry
        \begin{rSubsectionNoBullet}{\bf Master of Science in Business Analytics}{University of Illinois Urbana-Champaign}{Gies College of Business, Champaign, IL}{2022 - 2023}
            \italicitem{Graduated with Beta Gamma Sigma ($\mathcal{B}\Gamma\Sigma$) honor }
        \end{rSubsectionNoBullet}
        
        % Bachelor's degree entry
        \begin{rSubsectionNoBullet}{\bf Bachelor of Technology in Computer Science}{Rajasthan Technical University}{Poornima College of Engineering, Jaipur, India}{2015 - 2019}
            \italicitem{}
        \end{rSubsectionNoBullet}
        
    \end{rSection}
    
    \newpage
    %----------------------------------------------------------------------------------------
    % Technical skills section
    %----------------------------------------------------------------------------------------
    
    \tableEnv{Technical skills}{
        \entry{Project Domains}{Application Modernization, Enterprise Integration, Data Engineering, Infrastructure as Code, API Design}
        \entry{Integration Services}{Azure Functions, Azure Logic Apps, Azure Service Bus, Azure Event Grid, Azure API Management, Azure App Services, Azure Storage Services}
        \entry{Integration Platforms}{Databricks, Azure Data Factory, Dell Boomi, Google Data Fusion, Apache Airflow}
        \entry{DevOps Tools}{Azure DevOps, Jira, Docker, Git}
        \entry{Frameworks and Libraries}{FastAPI, PySpark, Selenium, Matplotlib, Pandas, Numpy}
        \entry{Languages}{Python, Go, Shell, Terraform, DAX, R, SQL}
    }
    
    %----------------------------------------------------------------------------------------
    % Projects
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Projects}
            \begin{itemize}
            \item \textbf{Integration Modernization (for a Snacks Manufacturer at Hanover,PA)} (09/2023 - Present):
            \begin{itemize}
                \item Role: Onsite Architect, leading a team of 15
                \item Description: Initially grappling with challenges in harmonizing integration patterns due to an early adoption of hybrid cloud strategies, our intervention paved the way for a streamlined, standardized approach. We executed the development of comprehensive standards and design documentation, focusing on Azure Services, Azure DevOps workflows, development protocols, security, as well as logging and alerting frameworks. We crafted libraries and frameworks to ensure adherence to these standards. This initiative modernized over 20 integrations, markedly enhancing their performance, stability, maintainability, development velocity, and testing cycles.
                \item Achievements: Successfully deployed Supply and Demand Planning data pipelines, establishing a reusable, well-defined batch data integration framework, marking a significant milestone in the project’s progress. 
            \end{itemize}
        \end{itemize}

            \begin{itemize}
            \item \textbf{Modernizing Financial Data Life-cycle (for University of Illinois Urbana-Champaign)} (10/2023 - 04/2024):
            \begin{itemize}
                \item Role: Lead Developer, lead a team of 6
                \item Description: The project aimed at addressing inefficiencies in the University of Illinois' billing process by modernizing the CFOP (data management through cloud integration. Leveraging AWS services (Lambda, DynamoDB, CloudWatch), we developed an automated solution to streamline CFOP updates and queries, eliminating manual interventions and significantly reducing operational delays. The solution included developing interactive forms for business users, consolidating APIs, and ensuring data security and integrity. This project was executed as part of the Business Practicum during the MSBA degree.
                \item Achievements: Successfully implemented solution, resulting in operational efficiency and enhanced data accuracy. The project was recognized for its innovative approach and selected for presentation at the UIUC Spring 2023 IT Pro Forum, highlighting the potential for process excellence through technology.
            \end{itemize}
        \end{itemize}

        \begin{itemize}
            \item \textbf{IPaaS on Azure (for a Hospitality Company at San Diego)} (10/2020 - 07/2022):
            \begin{itemize}
                \item Role: Lead Offshore Developer, lead a team of 8
                \item Description: The customer wanted to eliminate point to point custom data integration solution with a unified and extendable platform. Designed and developed an integration platform on Azure. The project included C\# based server-less functions, API Gateway, Cloud-based automated workflows and Infrastructure as Code all deployed and configured with CI/CD Pipelines for automation and agility.
                \item Achievements: Finished phase one of the project by going live as part of a company wide technology makeover effort.
            \end{itemize}
        \end{itemize}

        \begin{itemize}
            \item \textbf{Data Landscape Modernization (for an Illinois-based Motorparts Manufacturer)} (04/2021 - Present):
            \begin{itemize}
                \item Role: Architect and Lead Developer, lead a team of 6
                \item Description: Modernized the customer's data ingestion landscape by implementing batched data pipelines using Azure Data Factory and eliminating the need for any 3rd party middle-ware saving thousands of dollars in licensing costs. Established mechanisms to consolidate and move data from multiple SAP S/4 instances into Salesforce as aggregates to enable sales order reporting.
            \end{itemize}
        \end{itemize}
        
        \begin{itemize}
            \item \textbf{Data Landscape Modernization (for a Medical Imaging Device Manufacturer in Manhattan)} (10/2020 - Present):
            \begin{itemize}
                \item Role: Architect and Lead Developer, lead a team of 6
                \item Description: Modernized the customer's data landscape by moving from legacy on-premise database to a managed cloud database on Microsoft Azure, bringing down operational and management cost by $\sim$40\%. Established batch and real-time data ingestion pipelines from SAP C4C to Azure SQL Database with monitoring using in a Server-less fashion, well-defined procedures for deployment and release using Azure DevOps to ensure collaboration and quality control.
            \end{itemize}
        \end{itemize}
        
        \begin{itemize}
            \item \textbf{Data Integration on Dell Boomi (for a Global Sports Brand)} (05/2020 - 08/2020):
            \begin{itemize}
                \item Role: Lead Offshore Developer, lead a team of 4
                \item Description: Managed overall offshore delivery, and produced planning and design documents. Developed integrations connecting 10+ systems to run on daily batches and real-time frequencies using Dell Boomi Integration platform as a middle-ware.
            \end{itemize}
        \end{itemize}
        
        \begin{itemize}
            \item \textbf{Learning and Development Reporting (for an Indian Telecom Company)} (04/2019 - 04/2020):
            \begin{itemize}
                \item Role: Lead Developer, lead a team of 2
                \item Description: The project delivered a Power BI dashboard showing learning and development progress and metrics on the entire company. This solution is built to automatically pull the data from the company's various learning platforms, transformed and stored into Azure SQL Database. The data pipelines were built upon API and Selenium-based scheduled jobs.
            \end{itemize}
        \end{itemize}
        
    \end{rSection}
    
    %----------------------------------------------------------------------------------------
    %   Academic Research
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Academic Research}
        \begin{itemize}
            \item \textbf{Decentralized storage with Filecoin}: This research aims to provide public universities with a better understanding of the role of decentralized storage protocols in their IT infrastructure, specifically Filecoin/IPFS. The team plans to evaluate which public data sets are suitable for storage using Filecoin, demonstrate a use case of decentralized computing over the data, and create an analytical model that shows the cost-benefit trade offs of using decentralized storage. The output of this research provides universities with valuable insights into the potential benefits and risks of adopting decentralized storage solutions, allowing them to make more informed decisions about their IT infrastructure.
            \item \textbf{Creating LLM-based Dynamic Analytics on CRM and ERP Systems}: This research aims to develop a system that can create dynamic queries and visualizations based on user input and apply natural language processing (NLP) to Customer
            Relationship Management (CRM) and Enterprise Resource Planning (ERP) systems. The project 
            will involve analyzing large amounts of data from various sources using LLaMA (Large 
            Language Model Meta AI) model and fine-tuning LLMs to specialized queries. The generated 
            queries will be used to create dynamic visualizations, providing users with real-time insights 
            into their CRM and ERP systems. The project used National Center for Super computing Applications Delta supercomputer at UIUC for compute.
        \end{itemize}
    \end{rSection}
    
    %----------------------------------------------------------------------------------------
    % Certifications
    %----------------------------------------------------------------------------------------
    
    \tableEnv{Certifications}{
        \entry{}{Databricks Lakehouse Fundamentals, Azure Developer Associate, Datacamp Supervised Learning, Exploring and Producing Data for Business Decision Making, Inferential and Predictive Statistics for Business, Azure Data Fundamentals, Azure Fundamentals}
    }
    
    
    %----------------------------------------------------------------------------------------
    %   Honors, Achievements and Activities
    %----------------------------------------------------------------------------------------
    
    \begin{rSection}{Other Achievements and Activities}
        \begin{itemize}
            \item \textbf{Academic Excellence Award}, Issued by Gies College of Business - May 2023 \\
            Associated with University of Illinois Urbana-Champaign. This award signifies recognition as a distinguished student for outstanding academic achievements.
            \item \textbf{Lifetime Member}, Issued by Beta Gamma Sigma - Apr 2023 Associated with University of Illinois Urbana-Champaign. CH-34C-3046335. This distinction marks a lifetime membership in Beta Gamma Sigma, the international business honor society that recognizes the top 20 of graduate students in business schools accredited by The Association to Advance Collegiate Schools of Business (AACSB) worldwide.
            \item \textbf{Member of Jury, Manipal National Hackathon (DoIT)}: Mentored and evaluated innovative projects presented by tech students from all over the India in the 24Hr hackathon organised by Department of IT Rajasthan Gov and Manipal University
            \item \textbf{Mentor and Judge, JECRC Hackathon 4.0 (2020)}: Mentored and evaluated innovative projects presented by tech students from all over the India in the 24Hr hackathon organised by JECRC College, Jaipur
            \item \textbf{Expert Lectures at Various Universities}: Delivered multiple expert lectures on Cloud Services, Servelress computation and Modern API Design at University of Illinois Urbana-Champaign, MNIT Jaipur and Manipal University
        \end{itemize}
    \end{rSection}
    
\end{document}